Generalized Plackett-Luce Likelihoods

### 2022-09-27 inst/jss_hyper3.Rnw
fixes #164
fixes #161

The Fisher information for such observations has a minimum of
$\frac{68}{9}\simeq 7.56$ at $a=\frac{1}{2}$.  An inference problem
for a dataset including nonfinishers will be given below in
section~\ref{f1}.

@@

The ideas presented above may be extended to more than two types of
competitors.  Consider the following table, drawn from the men's
javelin, 2020 Olympics:

@@

Above we see that Chopra threw the longest and second-longest throws
of 87.58m and 87.03 respectively; Vadlejch threw the third-longest
throw of 86.67m, and so on (\code{NA} entries correspond to
no-throws.)  The attempts table may be converted to a \code{hyper3}
object, again using function \code{attemptstable2supp3()} but this
time passing \code{give.supp=TRUE}:

@@

Formula 1 motor racing is an important and prestigious motor sport
\citep{codling2017,jenkins2010}.  In Formula 1 Grand Prix, the
constructors' championship takes place between {\em manufacturers} of
racing cars (compare the drivers' championship, which is between
drivers).  In this analysis, the constructor is the object of
inference.  Each constructor typically fields two cars, each of which
separately accumulates ranking-based points at each venue.  Here we
use generalized Plackett-Luce to assess the constructors' performance.
The following table, included in the \code{hyper2} package as a
dataset, shows rankings for the first 9 venues of the 2021 season:

@@

\bibliography{chess}
\end{document}

>>>>

The Fisher information for such observations has a minimum of
$\frac{68}{9}\simeq 7.56$ at $a=\frac{1}{2}$.  An inference problem
for a dataset including nonfinishers will be given below in
Section~\ref{f1}.

@@

The ideas presented above may be extended to more than two types of
competitors.  Consider the following Table, drawn from the men's
javelin, 2020 Olympics:

@@

Above we see that Chopra threw the longest and second-longest throws
of 87.58m and 87.03 respectively; Vadlejch threw the third-longest
throw of 86.67m, and so on (\code{NA} entries correspond to
no-throws.)  The attempts Table may be converted to a \code{hyper3}
object, again using function \code{attemptstable2supp3()} but this
time passing \code{give.supp=TRUE}:

@@

Formula 1 motor racing is an important and prestigious motor sport
\citep{codling2017,jenkins2010}.  In Formula 1 Grand Prix, the
constructors' championship takes place between {\em manufacturers} of
racing cars (compare the drivers' championship, which is between
drivers).  In this analysis, the constructor is the object of
inference.  Each constructor typically fields two cars, each of which
separately accumulates ranking-based points at each venue.  Here we
use generalized Plackett-Luce to assess the constructors' performance.
The following Table, included in the \code{hyper2} package as a
dataset, shows rankings for the first 9 venues of the 2021 season:

@@

\bibliography{jss_hyper3}
\end{document}
